%-------------------------
% Resume in Latex
% Author : Owen Sheed
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Owen Sheed} \\ \vspace{1pt}
  \small 203-571-2099 $|$
  \href{mailto:osheed@elon.edu}{\uline{osheed@elon.edu}} $|$ 
  \href{https://www.linkedin.com/in/owensheed/}{\uline{linkedin.com/in/OwenSheed}} $|$
  \href{https://github.com/SheedGuy}{\uline{github.com/SheedGuy}}
\end{center}



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Elon University}{Elon, NC}
      {Bachelor of Science in Computer Science, Minor in Data Analytics}{Aug. 2020 -- May 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Intern}{June 2023 -- July 2023}
      {Equiniti Trust Company}{New York, NY}
      \resumeItemListStart
        \resumeItem{Developed a REST API in ASP.NET Core for user data, integrating JWT authentication, log4net logging, and async endpoints; stress-tested using a multithreaded Python script.}
        \resumeItem{Constructed a tool that parsed log files to produce detailed Excel reports, with features like error-specific reporting and SMTP-driven email delivery.}
        \resumeItem{Acquired in-depth proficiency in C\# and .NET, focusing on advanced features like lambda expressions, asynchronous functions, and secure data handling techniques.}
        \resumeItem{Strengthened abilities in effective communication, rapid learning, and problem-solving, coupled with insights into the finance industry, particularly regarding funds and transfer agents.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Project Manager}{March 2022 -- July 2022}
      {EJB Investments}{Miami, FL}
      \resumeItemListStart
        \resumeItem{Played a pivotal role in the successful release of a combined art and utility NFT collection, securing a 5-minute sellout, 30 ETH in volume, and 1.2k verified holders.}
        \resumeItem{Conducted comprehensive investment analyses, fostering relationships with potential investors, thereby facilitating funding for multiple investment ventures.}
        \resumeItem{Personally designed and built high-performance computers tailored for demanding applications, resulting in over a 151\% speed enhancement, accelerating mission-critical processes.}
        \resumeItem{Oversaw a marketing team that grew a Twitter audience to 70k followers. Led an NFT sticker campaign, distributing branded stickers to ambassadors in major cities, sparking widespread social media engagement.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Open Data Service} $|$ \emph{Go, Chi Router, PostgreSQL, Logrus}}{February 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Backend development for service, focusing on the ``Applications'' module, leveraging the Chi router and PostgreSQL for efficient data handling.}
            \resumeItem{Designed key CRUD operations for user applications, from registration to revocation.}
            \resumeItem{Enhanced error handling and logging using the Logrus library, ensuring system resilience and ease of debugging.}
            \resumeItem{Employed the Mockery library for rigorous testing, ensuring code reliability and robustness.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Protein Folding Simulation} $|$ \emph{C, Pthreads, Performance Tuning and Analysis}}{February 2023 -- March 2023}
          \resumeItemListStart
            \resumeItem{Developed a program to calculate the maximum number of H-H contacts in a given n-length protein, exhaustively walking every possible protein fold.}
            \resumeItem{Enhanced performance by multithreading with PThreads and aggressively optimizing base code such that each n-length protein only needs to score $3^{n-2}$ walks as opposed to the $4^{n-1}$ walks in the original.}
            \resumeItem{Achieved notable speed improvements: a 12-character protein previously took 132.98s, while the optimized parallel version completed in just 0.0269s. On average, the optimized parallel program decreased runtime by over 99\%.}
            \resumeItem{Conducted comprehensive performance testing, utilizing python to write to Excel files for in-depth analysis and optimization metrics.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++/C\#, Go, JS, HTML, CSS, SQL (Postgres, MySQL), Arm Assembly, LaTeX} \\
     \textbf{Frameworks}{: .NET Framework, ASP.NET Core, Next.JS, Node.JS, OpenCL} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, PyCharm, IntelliJ, Anaconda, TablePlus, Postman, VMWare} \\
     \textbf{Libraries}{: pandas, NumPy, Pthreads, CUDA, MPI, Chi Router, Requests}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
